
```{r include=FALSE}
library(ggplot2)
library(assertthat)
```

## Boomsoort: `r unique(DataModel$BMS)`; Domein: `r unique(DataModel$BOS_BHI)`

DOMEIN_ID: `r unique(DataModel$DOMEIN_ID)`; Modeltype: `r unique(DataModel$Modeltype)`

RMSE = `r #round(unique(DataModel$RMSE),2)`; aantal bomen = `r unique(DataModel$nBomen)`;
aantal bomen in bruikbaar interval = `r unique(DataModel$nBomenInterval)`;
aantal bomen met omtrek > 0,5 m = `r unique(DataModel$nBomenOmtrek05)`

Model bruikbaar tussen de omtrekklassen met klassemiddens 
`r unique(DataModel$Q5k)` en 
`r unique(DataModel$Q95k)` m

```{r warning=FALSE}
alpha <- 1 / log(unique(DataModel$nBomen))
Grafiek <-
  ggplot(DataModel, aes(x = Omtrek, y = HOOGTE)) +
  geom_jitter(width = 0.03, height = 0, alpha = alpha, colour = "darkgreen") +
  #geom_line(aes(y = Hoogte), size = 1) +
  geom_linerange(aes(y = Hoogte, xmin = Omtrek - 0.03, xmax = Omtrek + 0.03),
                 size = 2) +
  scale_x_continuous(minor_breaks = seq(0.05, 2.35, 0.1))

print(Grafiek)
```

