---
title: "Domeincurve"
author: "Els Lommelen"
date: "`r Sys.Date()`"
output: html_document
---

```{r include=FALSE}
library(ggplot2)
library(assertthat)
```

## Boomsoort: `r unique(SelectieModel$BMS)`; Domein: `r unique(SelectieModel$BOS_BHI)`

DOMEIN_ID: `r unique(SelectieModel$DOMEIN_ID)`

__Potentiële problemen: `r unique(SelectieModel$Reden)`__

RMSE = `r round(unique(SelectieModel$rmseD),2)`; aantal bomen = `r unique(SelectieModel$nBomen)`;
aantal bomen in bruikbaar interval = `r unique(SelectieModel$nBomenInterval)`;
aantal bomen in bruikbaar interval met omtrek > 0,5 m = `r unique(SelectieModel$nBomenIntervalOmtrek05)`

Model bruikbaar tussen de omtrekklassen met klassenmiddens 
`r unique(SelectieModel$Q5k)` en 
`r unique(SelectieModel$Q95k)` m

```{r warning=FALSE}

Grafiek <-
  ggplot(SelectieModel,
         aes(x = Omtrek, y = HOOGTE, colour = TeControlerenAfwijking)) +
  scale_colour_manual(values = alpha(c("black", "red"))) +
  geom_jitter(width = 0.03, height = 0) +
  geom_line(aes(y = H_D_finaal, colour = CurveSlecht, linetype = "Domein"),
            size = 1) +
  geom_point(aes(y = H_D_finaal, colour = CurveSlecht),
             shape = 21, fill = "white", size = 2, stroke = 1) +
  scale_linetype_manual(name = "Model",
                        values = c("Vlaams" = "dashed", "Domein" = "solid")) +
  # geom_vline(xintercept = SelectieModel$Q5) +
  # geom_vline(xintercept = SelectieModel$Q95) +
  scale_x_continuous(minor_breaks = seq(0.05, 2.35, 0.1))#+
  # geom_vline(xintercept = SelectieModel$Omtrek_Buigpunt, colour = "red") +
  # geom_vline(xintercept = SelectieModel$Omtrek_Extr_Hoogte, colour = "red") #nolint

if (has_name(SelectieModel, "H_VL_finaal")) {
  Grafiek <- Grafiek +
    geom_line(aes(y = H_VL_finaal, linetype = "Vlaams"),
              colour = "black", size = 1)
}

print(Grafiek)
```

