---
title: "Domeincurve"
author: "Els Lommelen"
date: "`r Sys.Date()`"
output: html_document
---

```{r include=FALSE}
library(ggplot2)
```

##Boomsoort: `r unique(SelectieModel$BMS)`; Domein: `r unique(SelectieModel$BOS_BHI)`

DOMEIN_ID: `r unique(SelectieModel$DOMEIN_ID)`

__Slechte curve omdat: `r unique(SelectieModel$Reden)`__

RMSE = `r unique(SelectieModel$rmseD)`; aantal bomen = `r unique(SelectieModel$nBomen)`;
aantal bomen in bruikbaar interval = `r unique(SelectieModel$nBomenInterval)`;
aantal bomen met omtrek > 0,5 m = `r unique(SelectieModel$nBomenOmtrek05)`;
`r unique(SelectieModel$PAfwijkend)`

(Rood = aandachtspunten, Blauw = Vlaams model)

```{r warning=FALSE}


Grafiek <- 
  ggplot(SelectieModel, aes_(x = ~Omtrek, y = ~HOOGTE, colour = ~Afwijkend)) +
  scale_colour_manual(values = alpha(c("black","red"))) +
  geom_jitter(width = 0.03, height = 0) +
  geom_line(aes_(y = ~H_D_finaal, colour = ~CurveSlecht), size = 1) +
  geom_line(aes_(y = ~H_VL_finaal), colour = "blue") +
  geom_vline(xintercept = SelectieModel$Q5) + 
  geom_vline(xintercept = SelectieModel$Q95) #+
  # geom_vline(xintercept = SelectieModel$Omtrek_Buigpunt, colour = "red") +
  # geom_vline(xintercept = SelectieModel$Omtrek_Extr_Hoogte, colour = "red")


print(Grafiek)
  

```

